scikit-image: Image processing in Python

### 2014-03-31 paper.tex
Move references to article format

We thank Timo Friedrich and Jan Kaslin for providing the zebrafish lesion data.
Portions of the research reported in this publication was supported by the
National Institute of Diabetes and Digestive and Kidney Diseases of the National
Institutes of Health under award number F30DK098832. The content is solely the
responsibility of the authors and does not necessarily represent the official
views of the National Institutes of Health.
\begin{thebibliography}{scipylecturenotes}
\bibitem[ohloh]{ohloh}{

Scikit-image on Ohloh, \url{https://www.ohloh.net/p/scikit-image}}
\bibitem[numpy]{numpy}{

van der Walt S, Colbert CS, and Varoquaux G, 2011. \textquotedbl{}The NumPy
array: a structure for efficient numerical computation\textquotedbl{}, Computing in
Science \& Engineering 13(2):22-30.}
\bibitem[ipython]{ipython}{

Pérez F, and Granger BE, 2007. IPython: A System for
Interactive Scientific Computing, Computing in Science and Engineering,
9(3):21-29. doi:10.1109/MCSE.2007.53.}
\bibitem[Mahotas]{Mahotas}{

Coelho, L.P. 2013. Mahotas: Open source software for scriptable
computer vision. Journal of Open Research Software 1(1),
DOI: \url{http://dx.doi.org/10.5334/4}}
\bibitem[scikit-learn]{scikit-learn}{

Pedregosa F, Varoquaux G, Gramfort A, Michel V, Thirion B,
Grisel O, Blondel M, Prettenhofer P, Weiss R, Dubourg V, Vanderplas J,
Passos A, Cournapeau D, Brucher M, Perrot M, and Duchesnay E, 2011.
Scikit-learn: machine learning in Python. Journal of Machine Learning
Research 12:2825-2830.}
\bibitem[pypi]{pypi}{

scikit-image 0.9.3 at the Python Package Index.
\url{https://pypi.python.org/pypi/scikit-image}}
\bibitem[anaconda]{anaconda}{

The Anaconda Scientific Python Distribution.
\url{https://store.continuum.io/cshop/anaconda/}}
\bibitem[canopy]{canopy}{

Enthought Canopy.
\url{https://www.enthought.com/products/canopy/}}
\bibitem[pythonxy]{pythonxy}{

Python(x,y). \url{https://code.google.com/p/pythonxy/}}
\bibitem[neurodebian]{neurodebian}{

python-skimage at NeuroDebian.
\url{http://neuro.debian.net/pkgs/python-skimage.html}}
\bibitem[ubuntu]{ubuntu}{

python-skimage in Ubuntu.
\url{http://packages.ubuntu.com/search?keywords=python-skimage}}
\bibitem[gsoc]{gsoc}{

Google Summer of Code.
\url{https://developers.google.com/open-source/soc}}
\bibitem[Canny]{Canny}{

Canny J, 1986. A Computational Approach To Edge Detection. IEEE
Trans. Pattern Analysis and Machine Intelligence 8:679-714}
\bibitem[BSD]{BSD}{

\url{http://www.gnu.org/licenses/license-list.html\#ModifiedBSD}}
\bibitem[GitHub]{GitHub}{

\url{https://github.com/scikit-image/scikit-image}}
\bibitem[GoogleGroups]{GoogleGroups}{

\url{https://groups.google.com/forum/?&fromgroups\#!forum/scikit-image}}
\bibitem[Cython]{Cython}{

Behnel S, Bradshaw R, Citro C, Dalcin L, Seljebotn DS, and Smith K,
2011. Cython: The best of both worlds. Computing in Science \& Engineering
13(2):31-39.}
\bibitem[TravisCI]{TravisCI}{

\url{https://travis-ci.org}}
\bibitem[Coveralls]{Coveralls}{

\url{https://coveralls.io}}
\bibitem[PEP8]{PEP8}{

\url{http://www.python.org/dev/peps/pep-0008/}}
\bibitem[NumpyDoc]{NumpyDoc}{

\url{https://github.com/numpy/numpy/blob/master/doc/HOWTO_DOCUMENT.rst.txt}}
\bibitem[flake8]{flake8}{

\url{https://pypi.python.org/pypi/flake8}}
\bibitem[Sphinx]{Sphinx}{

\url{http://sphinx-doc.org/}}
\bibitem[Versioning]{Versioning}{

\url{http://en.wikipedia.org/wiki/Software_versioning}}
\bibitem[SourceCode]{SourceCode}{

\url{https://github.com/scikit-image/scikit-image}}
\bibitem[DirectX]{DirectX}{

\url{http://msdn.microsoft.com/en-us/library/windows/desktop/dd607323\%28v=vs.85\%29.aspx}}
\bibitem[OpenGL]{OpenGL}{

\url{https://www.khronos.org/registry/gles/specs/2.0/es_full_spec_2.0.25.pdf}}
\bibitem[GraphicsGemsI]{GraphicsGemsI}{

Paeth, AW. Proper Treatment of Pixels as Integers, p. 249-256, code: p. 719}
\bibitem[APIdocs]{APIdocs}{

\url{http://scikit-image.org/docs/dev/}}
\bibitem[Bhatt04]{Bhatt04}{

Bhatt DH, Otto SJ, Depoister B, and Fetcho JR, 2004. Cyclic AMP-Induced Repair of Zebrafish Spinal Circuits. Science, 305:254-258. doi:10.1126/science.1098439}
\bibitem[Thuret06]{Thuret06}{

Thuret S, Moon LDF, and Gage FH, 2006. Therapeutic interventions after spinal cord injury. Nature Rev Neurosci, 7:628-643. doi:10.1038/nrn1955}
\bibitem[sciencefair]{sciencefair}{

\url{http://science-fair.org/database/project_awards.php?schoolname=Privately+Sponsored+Project&school_year=2014}}
\bibitem[scipylecturenotes]{scipylecturenotes}{

Scipy Lecture Notes, \url{http://scipy-lectures.github.io/}}
\bibitem[euroscipy2013]{euroscipy2013}{

EuroSciPy 2013 \url{https://www.euroscipy.org/2013/schedule/presentation/3/}}
\bibitem[pydata2012]{pydata2012}{

PyData 2012 \url{https://www.youtube.com/watch?v=Wvvxazwi2IY}}
\bibitem[cc-by]{cc-by}{

CC-BY license \url{http://creativecommons.org/licenses/by/4.0/}}
\bibitem[BTImaging]{BTImaging}{

BT Imaging, \url{http://www.btimaging.com}}
\bibitem[AICBT]{AICBT}{

Disguise Detection, \url{http://www.aicbt.com/disguise-detection/}}
\bibitem[ORB]{ORB}{

Ethan Rublee, Vincent Rabaud, Kurt Konolige and Gary Bradski \textquotedbl{}ORB: An
efficient alternative to SIFT and SURF\textquotedbl{}. Proceedings of the 2011
International Conference on Computer Vision (ICCV), pp.2564-2571.
doi: 10.1109/ICCV.2011.6126544}
\bibitem[ransac]{ransac}{

Martin A. Fischler and Robert C. Bolles. \textquotedbl{}Random Sample Consensus:
A Paradigm for Model Fitting with Applications to Image Analysis and
Automated Cartography\textquotedbl{}. Comm. of the ACM 24 (6): 381–395, June 1981.
doi:10.1145/358669.358692}
\bibitem[burt\_adelson\_0]{burt_adelson_0}{

P. Burt and E. Adelson. \textquotedbl{}A Multiresolution Spline With
Application to Image Mosaics\textquotedbl{}. ACM Transactions on Graphics, Vol. 2, No. 4,
October 1983. Pg. 217-236.}
\bibitem[burt\_adelson\_1]{burt_adelson_1}{

\textquotedbl{}The Laplacian Pyramid as a Compact Image Code\textquotedbl{}.
IEEE Transactions on Communications, April 1983.}
\bibitem[Enblend]{Enblend}{

Enblend 4.0 documentation, August 2010,
\url{http://enblend.sourceforge.net}.}
\end{thebibliography}

>>>>

We thank Timo Friedrich and Jan Kaslin for providing the zebrafish lesion data.
Portions of the research reported in this publication was supported by the
National Institute of Diabetes and Digestive and Kidney Diseases of the National
Institutes of Health under award number F30DK098832. The content is solely the
responsibility of the authors and does not necessarily represent the official
views of the National Institutes of Health.

\bibliography{refs}
